On singular elements in conformal field theory. \\ Singular elements in vertex operator algebras

### 2012-12-15 AffineLieAlgebras/MQFT2012/paper.tex
Minor changes
Some work on vertex algebra paper

Consider affine Lie algebra $\gfh$, which is an affine extension of (semi)simple Lie algebra $\gf$.
Let $\omega_{0},\dots,\omega_{r}$ be fundamental weights of $\gfh$. Then $L^{k\omega_{0}}_{\gfh}$ is vertex operator algebra and its irreducible modules are $L^{\mu}_{\gfh}$ such that $\mu<k$.

In this case Virasoro element is  $\omega=\frac{1}{2(k+h^{\vee})}\sum_i u_i(-1) u_i(-1)$, where
$u_i (i=1,\dots,\mathrm{dim}\gf)$  is an orthogonal basis in $\gfh$ w.r.t. Cartan-Killing form.

Vertex operator algebra structure for coset models of conformal field theory is given by the following statements \cite{frenkel1992vertex}:
\begin{statement}
\label{thm:cosets}
Let  $V=\bigoplus_{n=0}^{\infty} V_n$ -- vertex operator algebra such that $\mathrm{dim}V_0=1$ and $W\subset V$ is a subalgebra, denote by $\omega,\omega_1$ Virasoro elements of  $V$ and $W$ correspondingly. If the condition  $L_1\omega_1 =0$ is satisfied then $W'=\{b:
  a(n)b=0 \forall n\geq 0, a\in W\}$ is vertex operator subalgebra of  $V$ with Virasoro element $\omega'=\omega-\omega_1$.
\end{statement}
Note that for $\af\subset\gf$ and $V=L^0_{(\gf)}k, W=L^0_{(\af)k}$ the algebra
$W'$ is vertex operator algebra of  $G/A$-coset-model.

@@

\begin{itemize}
\item Singular element of simple Lie algebra irreducible module, VOA corresponding to that module.
  What are the relations in VOA on singular vectors? Is there BGG-resolution?
\item Affine Lie algebra, parabolic Verma modules?
\item Splints?
\item Coset vertex operator algebras and branching
\end{itemize}

>>>>

Consider affine Lie algebra $\gfh$, which is an affine extension of (semi)simple Lie algebra $\gf$.
Let $\omega_{0},\dots,\omega_{r}$ be fundamental weights of $\gfh$. Irreducible highest weight module $L^{k\omega_0}_{\gfh}$ of affine Lie algebra $\gfh$ can be endowed with the structure of Vertex operator algebra \cite{frenkel1992vertex}. Its irreducible modules are $L^{\mu}_{\gfh}$ such that $\mu<k$.  Virasoro element in this case is given by the formula
\begin{equation}
  \label{eq:2}
  \omega=\frac{1}{2(k+h^{\vee})}\sum_i u_i(-1) u_i(-1),
\end{equation}
where $u_i (i=1,\dots,\mathrm{dim}\gf)$  form an orthogonal basis in $\gfh$ with respect to Cartan-Killing form.

Vertex operator algebra structure for coset models of conformal field theory is given by the following statements \cite{frenkel1992vertex}:
\begin{statement}
\label{thm:cosets}
Let  $V=\bigoplus_{n=0}^{\infty} V_n$ -- vertex operator algebra such that $\mathrm{dim}V_0=1$ and $W\subset V$ is a subalgebra, denote by $\omega,\omega_1$ Virasoro elements of  $V$ and $W$ correspondingly. If the condition  $L_1\omega_1 =0$ is satisfied then $W'=\{b:
  a(n)b=0 \forall n\geq 0, a\in W\}$ is vertex operator subalgebra of  $V$ with Virasoro element $\omega'=\omega-\omega_1$.
\end{statement}
Note that for $\af\subset\gf$ and $V=L^0_{(\gf)}k, W=L^0_{(\af)k}$ the algebra
$W'$ is the vertex operator algebra of  $G/A$-coset-model.

@@

Irreducible $V$-modules can be reduced into combination of tensor products of irreducible $W$- and $W'$-modules:
\begin{equation}
  \label{eq:1}
  M_V=\bigoplus_{i\in I} (M^i_{W}\otimes M^i_{W'}),
\end{equation}
where $I$ is some index set.

For coset models we can write this decomposition as
\begin{equation}
  \label{eq:3}
  L^{\mu}_{\gfh}=\bigoplus_{\nu \in \pi({\cal N})} (M^{h(\mu,\nu),c}_{Vir} \otimes L^{\nu}_{\afh}),
\end{equation}
where the summation is over the projection of weight diagram of $L^{\mu}_{\gfh}$ to Cartan subalgebra of $\afh$. Central charge and conformal weights of Virasoro modules are equal to
\begin{eqnarray}
  \label{eq:4}
    c=\frac{k\;\mathrm{dim}\gf}{k+h^{\vee}_{\gf}}-\frac{x_e k\;\mathrm{dim}\af}{x_e k+h^{\vee}_{\af}}\\
    h(\mu,\nu)=\left(\frac{(\mu,\mu+2\rho)}{2(k+h^{\vee}_{\gf})}-\frac{(\nu,\nu+2\rho_{\af})}{2(k+h^{\vee}_{\gf})}\right)
\end{eqnarray}
(See pp. 837-840 (855-858 in file) of Di Francesco for a characterization of singular vectors of Virasoro modules for $su(2)$)

Let $V=L$
Branching functions coincide with characters of Virasoro modules. Virasoro characters can be written in terms of Virasoro Verma modules characters. 
Recurrence relations on branching coefficients lead to recurrence relations on integer partitions numbers.
\begin{itemize}
\item Singular element of simple Lie algebra irreducible module, VOA corresponding to that module.
  What are the relations in VOA on singular vectors? Is there BGG-resolution?
\item Affine Lie algebra, parabolic Verma modules?
\item Splints?
\item Coset vertex operator algebras and branching
\end{itemize}
